### 2015-02-24 paper_30_measure.tex
chapter 3 work

\section{EVALUATING AN SDO}

    Anything can be measured \cite{Hubbard2010}.  Thus, an SDO can be 
    measured.  Proper measurement is crucial for improvement because
    without a starting point it is impossible to determine progress.
    Also, consistent reporting is essential for 
    tracking historical performance.  Many methods are used
    to measure and evaluate SDOs.  Some of the common ones
    will be explained in this section.

    \subsection{METRICS}
        A \textit{metric} can be defined as the science of indirect measurement. Metrics
        are very common in the measurement of SDOs.  
        The following are some examples of metrics that can be collected 
        for an SDO. 
        \begin{itemize}
            \item SLOC - The number of Source Lines of Code 
            \item NOM - The Number of Methods per class
            \item Complexity - A numerical measure of the code complexity,
                some common examples are McCabe \cite{McCabe1976} and 
                Halstead \cite{Halstead1977}
            \item Design - The amount of coupling and cohesion present 
                in the software code
            \item Source Code Analysis - Tools that determine whether 
                code adheres to specified set of rules. Common 
                examples are PMD\footnote{PMD is a source code analysis product.  
                It is not an acronym.} and FindBugs$^{TM}$ \cite{PMD, Findbugs}.
        \end{itemize}
        All these metrics are beneficial, but none of them tell the story of the entire
        SDO.  Most of the metrics, as seen in the list above, around an SDO focus on 
        the source code and development phase. 
        Since metrics are indirect, it can be very difficult match SDO performance with
        a metric or series of metrics.  Metrics are great for tracking, but decision making
        based upon metrics is difficult.

    \subsection{INDICATORS}
        Indicators can be crucial measurements
        within any business setting, and an SDO is no exception. Determining
        the correct indicators for an organization can
        be difficult.  Software development organizations
        are no exception. 
        The differences between the indicators will be explored and
        possible measures for each indicator in an SDO will be
        presented.  Indicators are sometimes refered to as 
        performance measures \cite{parmenter2010}.  The four
        types of indicators important to an SDO are shown
        in Table \ref{tab:indicators}.

@@

        More information on the indicators can be found
        in chapter 1 of 
        as well as \cite{florac1999,kaplan1992}.

        \subsubsection{RESULT INDICATORS FOR SDO}
            This section will cover the potential result indicators for an SDO.

        \subsubsection{KEY RESULT INDICATORS FOR SDO}

        \subsubsection{PERFORMANCE INDICATORS FOR SDO}
            This section will cover the potential performance indicators for an SDO.

        \subsubsection{KEY PERFORMANCE INDICATORS FOR SDO}

        Antolic in \cite{Antolic2008} demostrates some ways to measure KPIs for the  software development process.

@@

        A common technique for organizations to measure themselves is a balanced scorecard.
        A \textit{balanced scorecard} must contain the following six
        characteristics.
        \begin{enumerate}
          \item Financial 
          \item Customer Focus
          \item Environment/Community
          \item Internal Process
          \item Employee Satisfaction
          \item Learning and Growth
        \end{enumerate}

>>>>

\section{MEASURING AN SDO}

    Anything can be measured \cite{Hubbard2010}.  Thus, an SDO can be 
    measured.  Proper measurement is crucial for improvement because
    without a starting point it is impossible to determine progress.
    Also, consistent reporting is essential for 
    tracking historical performance.

    The SDLC, like any process, needs to be properly measured.  In
    order to accomplish proper measurement, three activities need
    to occur \cite{florac1999}.

    \begin{itemize}
        \item Identify Process Issues
        \item Select And Define Measures
        \item Integrate with Software Process
    \end{itemize}

    This work will focus on steps 1 and 2.  The process issue is the overall
    effectiveness of the SDO.  Section \ref{sec:MPI} will cover step 2 as
    it relates to an SDO.  Step
    3 will be different for each SDO, but Section \ref{sec:SDLC-AE} provides
    a bit of guidance for storing the correct information.  It is up to the
    specific SDO to determine how and when the information is being stored.

    Many methods have been  used in the past 
    to measure and evaluate SDOs.  Some of the common methods
    will be explained in the following sections.

    \subsection{METRICS}
        A \textit{metric} can be defined as a means of telling a complete story
        for the purpose of improving something \cite{Klubeck2011}.  Metrics are
        frequently indirect measurements. Metrics
        are very common in the measurement of SDOs.  
        The following are some examples of metrics that can be collected 
        for an SDO. 
        \begin{itemize}
            \item SLOC - The number of Source Lines of Code 
            \item NOM - The Number of Methods per class
            \item Complexity - A numerical measure of the code complexity,
                some common examples are McCabe \cite{McCabe1976} and 
                Halstead \cite{Halstead1977}
            \item Design - The amount of coupling and cohesion present 
                in the software code
            \item Source Code Analysis - Tools that determine whether 
                code adheres to specified set of rules. Common 
                examples are PMD\footnote{PMD is a source code analysis product.  
                It is not an acronym.} and FindBugs$^{TM}$ \cite{PMD, Findbugs}.
        \end{itemize}
        All these metrics are beneficial, but none of them tell the story of the entire
        SDO.  Most of the metrics, as seen in the list above, for an SDO focus on 
        the source code and development phase. 
        Since metrics are indirect, it can be very difficult match SDO performance with
        a metric or series of metrics.  Metrics are great for tracking, but decision making
        based upon metrics alone is difficult.  That is why many of the other techniques
        build upon metrics to provide a more complete overall picture of an SDO.

    \subsection{INDICATORS}
        Another common measurement technique is indicators. An
        \textit{indicator} is simply a performance measure. 
        Typically, a number of indicators will be placed
        together and displayed in some report or on some
        dashboard. 
        Indicators can be crucial measurements
        within any business setting, and an SDO is no exception. Determining
        the correct indicators for an organization can
        be difficult, and many organizations incorrectly classify
        the indicators \cite{parmenter2010}.  
        The differences between the indicators will be explored and
        possible measures for each indicator in an SDO will be
        presented.   The four
        types of indicators important to an SDO are shown
        in Table \ref{tab:indicators}.

@@

        \subsubsection{RESULT INDICATORS FOR SDO}
            More to come.

        \subsubsection{KEY RESULT INDICATORS FOR SDO}
            More to come.

        \subsubsection{PERFORMANCE INDICATORS FOR SDO}
            More to come.

        \subsubsection{KEY PERFORMANCE INDICATORS FOR SDO}
            More to come.

        Antolic in \cite{Antolic2008} demonstrates some ways to measure KPIs for the  software development process.

@@

        A common technique for organizations to measure themselves is a balanced scorecard. \cite{kaplan1992}
        A \textit{balanced scorecard} must contain the following six
        characteristics.
        \begin{enumerate}
          \item Financial 
          \item Customer Focus
          \item Environment/Community
          \item Internal Process
          \item Employee Satisfaction
          \item Learning and Growth
        \end{enumerate}
